---
title: "Homework 3"
subtitle: "Research in Health Economics, Spring 2025"
author: "Sammy Ramacher"
format:
    pdf: 
        output-file: "RamacherS_hwk4-1"
        output-ext: "pdf"
        header-includes: 
            - \usepackage{float}
            - \floatplacement{table}{H}
knitr:
    opts_chunk:
        warning: false

---
```{r}
#| include: false
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra, broom)

            
```

```{r}
#| include: false
#| eval: true

final.data <- read_rds("data/output/final_ma_data.rds")
load("hwk4_workspace.Rdata")
```
The GitHub repository for this work is available [here](https://https://github.com/sramac9/Homework4).


\newpage
# Summarize the Data

\noindent Question 1. Remove all SNPs, 800-series plans, and prescription drug only plans (i.e., plans that do not offer Part C benefits). Provide a box and whisker plot showing the distribution of plan counts by county over time. Do you think that the number of plans is sufficient, too few, or too many?

```{r}
#| echo=FALSE, fig.show='hold'
plan.counts.plot
```
\newpage

\noindent Question 2. Provide bar graphs showing the distribution of star ratings in 2010, 2012, and 2015. How has this distribution changed over time?
```{r}
#| echo=FALSE, fig.show='hold'
star.dist.15
```
\newpage

\noindent Question 3. Plot the average benchmark payment over time from 2010 through 2015. How much has the average benchmark payment risen over the years?
```{r}
#| echo=FALSE, fig.show='hold'
bench.plt
```
\newpage

